---
title: "01_dataset_creation"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output:
  html_notebook:
    code_folding: hide
    number_sections: yes
    theme: flatly
    toc: yes
    toc_float: yes
knit: (function(inputFile, encoding) { rmarkdown::render(inputFile, encoding = encoding, output_file = paste0(substr(inputFile,1,nchar(inputFile)-4)," ",Sys.Date(),'.html')) })
editor_options: 
  markdown: 
    wrap: 72
---

# Environment

```{r}
#https://www.rdocumentation.org/packages/bigrquery/versions/0.4.1
knitr::opts_chunk$set(echo = TRUE)

library(dslabs)
library(dplyr)
library(tidyverse)
library(bigrquery)
library(readr)
library(httpuv)
library(odbc)
library(sqldf)
library(DBI)
library(comorbidity)
library(tableone)
library(dbplyr)
library(RPostgres)
library(reshape)
library(bayestestR)
library(weathermetrics)
library(ggthemes)
library(pROC)
library(caret)
library(knitr)
library(kableExtra)
library(stringr)
library(rmarkdown)
library(modelsummary)
library(bookdown)
library(scales)
library(glue)
library(extrafont)
library(DiagrammeR)
library(labelled)
library(DescTools)
library(MASS)
library(MLmetrics)
```


# Set up BigQuery related functions

This chunks also creates the run_query and get_sql function.

```{r setup, include=FALSE}
# Updated for our year
project_id <- "hst-953-2018"
options(httr_oauth_cache=FALSE)
# Function that takes in a sql command and runs it on bigquery
run_query <- function(query){
  data <- query_exec(query, project=project_id, use_legacy_sql=FALSE,max_pages = Inf)
  return(data)
}

# function for reading sql files
getSQL <- function(filepath){
  con = file(filepath, "r")
  sql.string <- ""

  while (TRUE){
    line <- readLines(con, n = 1)

    if ( length(line) == 0 ){
      break
    }

    line <- gsub("\\t", " ", line)

    if(grepl("--",line) == TRUE){
      line <- paste(sub("--","/*",line),"*/")
    }

    sql.string <- paste(sql.string, line)
  }

  close(con)
  return(sql.string)
}

'%!in%' <- function(x,y)!('%in%'(x,y))
```


# Loading queries and extracting the data

Loads all queries from the sql files in the extraction folder and runs them into RBigQuey to extract the data.


```{r}
apache <- run_query(getSQL("../extraction/apache.rdata")
ICDs <- run_query(getSQL("../extraction/ICDs.sql" ))
elixhauser <- run_query(getSQL("../extraction/elixhauser.sql")
demographics <- run_query(getSQL("../extraction/demographics.sql")
ventilationevents <- rrun_query(getSQL("../extraction/ventilationevents.sql")
labs <- run_query(getSQL("../extraction/labs.sql")
allBPs <-run_query(getSQL("../extraction/allBPs.sql")
demographics <- run_query(getSQL("../extraction/demographics.sql")
ventilationevents <- run_query(getSQL("../extraction/ventilationevents.sql")

comp <- left_join(allBPs, demographics, by = "patientunitstayid") %>% left_join(Elixhauser, by = "patientunitstayid") %>% left_join(apache, by = "patientunitstayid") %>% filter(!is.na(MAPauc))
```

```{r}
dialysislist <- unique(dialysis$patientunitstayid)
nondialysisBPs <- BPs %>% filter(!(patientunitstayid %in% dialysislist))
nondialysislistunique <- unique(nondialysisBPs$patientunitstayid)
nondialysislistuniqueSQL <- glue::glue_sql("{nondialysislistunique*}", .con = con2)

nondialysisNIBP <- select(nondialysisBPs, patientunitstayid, chartoffset, entryoffset, nibp_systolic, nibp_diastolic, nibp_mean)
colnames(nondialysisNIBP) <- c("patientunitstayid", "chartoffset", "entryoffset", "SBP", "DBP", "MAP")
nondialysisIBP <- select(nondialysisBPs, patientunitstayid, chartoffset, entryoffset, ibp_systolic, ibp_diastolic, ibp_mean)
colnames(nondialysisIBP) <- c("patientunitstayid", "chartoffset", "entryoffset", "SBP", "DBP", "MAP")

allBPs <- rbind(nondialysisNIBP, nondialysisIBP) %>% arrange(patientunitstayid, chartoffset) %>% group_by(patientunitstayid, chartoffset) %>% summarize(SBP = mean(SBP, na.rm = TRUE), DBP = mean(DBP, na.rm = TRUE), MAP = mean(MAP, na.rm = TRUE)) %>% group_by(patientunitstayid) %>% summarize(SBPauc = area_under_curve(chartoffset, SBP, method = "trapezoid", na.rm = TRUE), DBPauc = Area_Under_Curve(chartoffset, DBP, method = "trapezoid", na.rm = TRUE), MAPauc = area_under_curve(chartoffset, MAP, method = "trapezoid", na.rm = TRUE), starttime = min(chartoffset), endtime = max(chartoffset))

saveRDS(allBPs, file = "allBPs.rdata")

#BPcomplete <- rbind(nondialysisNIBP, nondialysisIBP) %>% arrange(patientunitstayid, chartoffset)

#BPcomplete[MAP < 65, diff(range(chartoffset)), by = patientunitstayid]
```




how frequently blood pressure measured, overall and stratified by race, by hospital
  adjust for age, illness severity, comorbidities
look at biggest hospital in eICU
hypotension as measured by other papers
comorbidities/illness serverity
